\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 evaluation.tex
add nobe and fix virt timer

Finding this bug was somewhat of a surprise. When two threads in the same process wait for a child to exit, they both block on the same condition variable, and one of them has a pointer to the other in its \texttt{cond\_queue\_next} pointer. However, when awakened, the condition variable code did not clear the value of this pointer. Fortunately, an assert statement in the thread destruction code caught that the pointer was non-\texttt{NULL} when it should have been \texttt{NULL}, and the kernel panicked.

>>>>

Finding this bug was somewhat of a surprise. When two threads in the same process wait for a child to exit, they both block on the same condition variable, and one of them has a pointer to the other in its \texttt{nobe->cond\_queue\_next} pointer. However, when awakened, the condition variable code did not clear the value of this pointer. Fortunately, an assert statement in the thread destruction code caught that the pointer was non-\texttt{NULL} when it should have been \texttt{NULL}, and the kernel panicked.

### 2012-05-18 futurework.tex
add nobe and fix virt timer

Finally, Landslide will need to find new ways to control non-deterministic events in the system. Since virtualised kernels use the same timer interrupt as the host they run on, Landslide \revision{will need to intercept it, and perhaps control the guest kernel's context switching with a custom ``Landslide-driven'' context switcher instead.}

>>>>

Finally, Landslide will need to find new ways to control non-deterministic events in the system. Since timer ticks in virtualised kernels are mediated by the hypervisor, Landslide \revision{may need to intercept the timer, and perhaps control the guest kernel's context switching with a custom ``Landslide-driven'' context switcher instead.}
